### 2021-03-26 chapters/sections/9-imp_utilization_in_ozg.tex
finished

This chapter presents an IMP solution which solves issues that OZG identity management has, as described in chapter 3. For utilization of IMP services as described by the IMP solution, an integration architecture will be presented that enables the OZG system architecture described in section 2.3 to access the IMP system described in section 2.2.

Focus of the IMP solution and the integration architecture is to require minimal invasion into the existing system architecture: Few existing system components should have to be modified and the existing operation of the system should not be disrupted. The IMP solution should provide an additional but optional way for users to access OZG services.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
    \caption{IMP Layer Diagram}
    \label{integration1:layer_diagram}
\end{figure}

@@

\paragraph{IMP Solution Layer} 
The IMP solution is integration on the use case level. It presents possibilities of leveraging interaction capabilities of the IMP system in the context of the Service Provider for improvement of usability, data protection and security. Furthermore it describes which types of relationships the Service Provider can use in their business scenario, how relationships can be processed, which types of messages can be exchanged through the relationships, what the purpose of each message can be and how the IMP client can react to different message types.

The IMP solution focuses on utilizing IMP capabilities in a way which affects the existing operation of the system architecture the least while solving as many identity management issues described in section 3.1 as possible.

@@

Focus of the Technological Integration is to connect with the minimal number systems possibly while solving as many integration issues described in section 3.3 as possible.

>>>>

This chapter presents an IMP solution which solves issues of user profile-based identity management by enabling users to create, manage, and access user profiles through IMP. For the utilization of IMP services as described by the IMP solution, an integration architecture is presented that enables the OZG system architecture described in section 2.2 to access the IMP system described in section 2.1.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
    \caption{IMP System Layers}
    \label{integration1:layer_diagram}
\end{figure}

@@

\paragraph{IMP Solution Layer} 
The IMP solution is integration on the use case level. It presents possibilities of leveraging the interaction capabilities of the IMP system in the context of the Service Provider for the improvement of usability, data protection and security. Furthermore, it describes which types of relationships the Service Provider can use in their business scenario, how relationships can be processed, which types of messages can be exchanged through the relationships, what the purpose of each message can be and how the IMP client can react to different message types.

@@

### 2021-03-26 msc-thesis.tex
finished

@@

@@

\chapter{Introduction}

\section{Context}

\subfile{sections/1-context}

\section{Objective}

\subfile{sections/2-objective}

\section{Structure of Work}

\subfile{sections/3-structure_of_work}

\chapter{Background and Related Work}

\section{Terminology}

\subfile{sections/4-terminology}

\section{Identity Management Provisioning (IMP)}

\subfile{sections/5-imp}

\section{Online Access Law (OZG)}

\subfile{sections/6-online_access_law}

\section{Messaging}

\subfile{sections/7-messaging}

\chapter{OZG Identity Management}

\subfile{sections/8-identity_management}

\chapter{IMP Utilization in OZG}

\subfile{sections/9-imp_utilization_in_ozg}

\chapter{Advanced Utilization}

\subfile{sections/12-advanced_utilization}

\chapter{Solution Evaluation}

\section{Conclusion}

\chapter{Outlook: Advanced IMP Integration}

>>>>

Diese Bachelorarbeit stellt Identity Management Provisioning (IMP) als mögliche Lösung von Problemen Benutzerprofil basierter Identitätsmanagementsysteme vor. IMP bietet Identitätsmanagement als Service für Benutzer und Dienstanbieter. Es ermöglicht Nutzern eine IMP Identität zu erstellen, um persönliche Informationen und Nachrichten mit mehreren Dienstanbietern auszutauschen.

Damit Dienstanbieter mit bestehenden, auf Benutzerprofilen basierenden Identitätsmanagementsystemen IMP nutzen können, ist eine Integration in bestehende Geschäftsprozesse und bestehende Systemarchitekturen erforderlich. Es werden zwei IMP Lösungen vorgestellt, die beschreiben, wie Service Provider IMP verwenden können. Außerdem wird ein Messaging System für die technologische Integration präsentiert.

Ziel der IMP Lösungen ist es, Möglichkeiten zu beschreiben, die Benutzerfreundlichkeit, Datenschutz und Sicherheit des Identitätsmanagements durch die Nutzung des IMP Dienstes erhöhen. Die IMP-Lösungen werden, basierend auf dem aktuell relevanten Anwendungsfall des Online-Zugangs-Gesetzes (OZG), konzipiert.

Die erste IMP Lösung beschreibt eine Möglichkeit, welche Benutzern die Erstellung von Benutzerprofilen, Pflege persönlicher Informationen und Interaktion über eine IMP Anwendung ermöglicht. Dieser Integrationsansatz soll die Benutzerfreundlichkeit erhöhen und gleichzeitig das Risiko, die Komplexität und die Kosten der Integration minimieren. Dadurch, dass auf Benutzerprofilen basierende Identitätsmanagementsysteme in Betrieb gelassen werden, bleiben Probleme hinsichtlich des Datenschutzes bestehen. Eine zweite IMP Lösung wird vorgestellt, die den Datenschutz erhöht, indem Benutzerprofile ersetzt werden. Stattdessen geben Nutzer persönliche Informationen nur für einzelne Geschäftsprozesse temporär frei.

Zur Integration von IMP Lösungen wird ein Messaging System vorgestellt, das in der Lage ist, IMP in bestehende Systemarchitekturen von Dienstanbietern zu integrieren. Neben messaging ermöglicht ein modularer Ansatz, dass die Integrationsarchitektur konfigurierbar und erweiterbar ist, um verschiedene IMP Lösungen in unterschiedliche Systemarchitekturen zu integrieren. Die Fähigkeiten des Messaging Systems werden durch die Integration der zuvor beschriebenen, grundsätzlich unterschiedlichen, IMP Lösungen in verschiedene Systemarchitekturen im Kontext des OZG demonstriert.

@@

This bachelor thesis presents Identity Management Provisioning (IMP) as a possibility for solving problems of user profile-based identity management systems. IMP provides identity management as a service to users and Service Providers. It enables users to create an IMP identity and use it to share personal information and exchange messages with multiple Service Providers.

In order for Service Providers with existing user profile-based identity management systems to utilize IMP, integration into their existing business processes and existing system architectures is necessary. Two IMP solutions which describe how Service Providers can utilize IMP and one messaging system for technological integration are presented.

The purpose of IMP solutions is to describe possibilities to increase usability, data protection and security of identity management through the utilization of the IMP service. The IMP solutions are designed, based on the currently relevant use case of the Online Access Law (Online Zugangs Gesetz - OZG).

The first IMP solution describes the possibility of enabling users to create user profiles, maintain personal information, and interact through an IMP application. This integration approach is designed to increase usability while minimizing the risk, complexity, and cost of integration.
As a result of leaving user profile-based identity management in operation, problems regarding data protection remain. A second IMP solution is presented to increase data protection by replacing user profiles. Instead, users temporarily share personal information for individual business processes.

For the integration of IMP solutions, a messaging system is presented which is capable of integrating IMP into existing system architectures of Service Providers. In addition to messaging, a modular approach enables the integration architecture to be configurable and expandable to integrate various IMP solutions into different system architectures.

The capabilities of the messaging system are demonstrated by integrating the previously described, fundamentally different IMP solutions into different system architectures in the context of the OZG.

@@

\chapter{Introduction}
\subfile{chapters/1-introduction}

\chapter{Background and Related Work} \label{chapter:background}
\subfile{chapters/2-background_and_related_work}

\chapter{User Profile Identity Management} \label{chapter:user_profile_identity_management}
\subfile{chapters/3-ozg_identity_management}

\chapter{IMP Utilization as Extension}
\subfile{chapters/4-imp_utilization_in_ozg}

\chapter{IMP Utilization as Replacement}
\subfile{chapters/5-advanced_utilization}

\chapter{Conclusion}
\subfile{chapters/6-conclusion}
